Dependent Object Types

### 2012-09-22 doc/fool/article.tex
rev

\begin{abstract}
We propose a new type-theoretic foundation of Scala and languages like
it: the Dependent Object Types (DOT) calculus. DOT models Scala's
path-dependent types, abstract type members and its mixture of nominal
and structural typing through the use of refinement types. The core
formalism makes no attempt to model inheritance and mixin
composition. DOT normalizes Scala's type system by unifying the
constructs for type members and by providing classical intersection
and union types which simplify Scala's compound types and glb/lub
computations.

@@

\subsection{Glbs and Lubs}\label{ex-exp}

@@

>>>>

\begin{abstract}
We propose a new type-theoretic foundation of Scala and languages like
it: the Dependent Object Types (DOT) calculus. DOT models Scala's
path-dependent types, abstract type members and its mixture of nominal
and structural typing through the use of refinement types. The core
formalism makes no attempt to model inheritance and mixin
composition. DOT normalizes Scala's type system by unifying the
constructs for type members and by providing classical intersection
and union types which simplify glb/lub computations.

@@

\subsection{Glbs and Lubs}

@@

Note that expansions do not always exist. %TODO
